logit

### 2021-12-05 logit.Rmd
some changes

>>>>

train$ChestPainType <- as.factor(train$ChestPainType)
train$Sex <- as.factor(train$Sex)
train$FastingBS <- as.factor(train$FastingBS)
train$RestingECG <- as.factor(train$RestingECG)
train$ExerciseAngina <- as.factor(train$ExerciseAngina)
train$ST_Slope <- as.factor(train$ST_Slope)
train$HeartDisease <- as.factor(train$HeartDisease)

test$ChestPainType <- as.factor(test$ChestPainType)
test$Sex <- as.factor(test$Sex)
test$FastingBS <- as.factor(test$FastingBS)
test$RestingECG <- as.factor(test$RestingECG)
test$ExerciseAngina <- as.factor(test$ExerciseAngina)
test$ST_Slope <- as.factor(test$ST_Slope)
test$HeartDisease <- as.factor(test$HeartDisease)
